Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-25 paper/paper.tex
Iterate section 2
Iterate section 3

There exists another layer on top of the directory-bucketed key-value mappings,
i.e., schematized \emph{semi-relational} tables. This layer is probably the most
intuitive one for people who are used to common database systems. The data model
allows applications to create databases in a universe each of which may contain
an arbitrary number of schematized semi-relational tables. A table has rows,
columns, and (as a third dimension) versioned values. Spanner's tables are
semi-relational because rows must have names, i.e., every table must have an
ordered set of one or more primary-key columns. This is useful for applications
because the locality of data can be controlled by choosing keys accurately.

@@

TrueTime represents time as a $TTinterval$. A $TTinterval$ is an interval with a
bounded time uncertainty and has two endpoints, $earliest$ and $latest$, which
are of type $TTstamp$ (a timestamp in the context of Spanner).
Table~\ref{tbl:truetime-api} summarizes the three methods provided by the TrueTime
API. However, the most important method is $TT.now()$. i$TT.now()$ which returns
a $TTinterval$ which is guaranteed to contain the absolute time of the invocation
of $TT.now()$, i.e., $TT.now().earliest \leq t_{abs}(e) \leq TT.now().latest$,
where $e$ denotes the event of invoking $TT.now()$. More precisely, the absolute
time of invocation of $TT.now()$ is exactly in the middle this $TTinterval$. The
interval itself spans over $2\cdot\epsilon$, where $\epsilon$ denotes the
instantaneous error bound. $\epsilon$ is derived from applied worst-case local
clock drift (assumed to be $200\mu$s/sec). This instantaneous error bound is
adjusted over time for every single machine.

>>>>

There exists another layer on top of the directory-bucketed key-value mappings,
i.e., schematized \emph{semi-relational} tables. This layer is probably the most
intuitive one for people who are used to common database systems. The data model
allows applications to create databases in a universe each of which may contain
an arbitrary number of schematized semi-relational tables. A table has rows,
columns, and versioned values. Spanner's tables are semi-relational because rows
must have names, i.e., every table must have an ordered set of one or more
primary-key columns. This is useful for applications because the locality of data
can be controlled by choosing keys accurately.

@@

TrueTime represents time as a $TTinterval$. A $TTinterval$ is an interval with a
bounded time uncertainty and has two endpoints, $earliest$ and $latest$, which
are of type $TTstamp$ (a timestamp in the context of Spanner).
Table~\ref{tbl:truetime-api} summarizes the three methods provided by the TrueTime
API. However, the most important method is $TT.now()$. $TT.now()$ returns a
$TTinterval$ which is guaranteed to contain the absolute time of the invocation
of $TT.now()$, i.e., $TT.now().earliest \leq t_{abs}(e) \leq TT.now().latest$,
where $e$ denotes the event of invoking $TT.now()$. More precisely, the absolute
time of invocation of $TT.now()$ is exactly in the middle this $TTinterval$. The
interval itself spans over $2\cdot\epsilon$, where $\epsilon$ denotes the
instantaneous error bound. $\epsilon$ is derived from applied worst-case local
clock drift (assumed to be $200\mu$s/sec). This instantaneous error bound is
adjusted over time for every single machine.
